DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.4.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{itemize}
\item \textbf{Representation}: the synthesis can be performed for digital systems specified as transfer-function or state-space equations;
\item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis can be executed via command-line or graphical-user interface (GUI). For the GUI application, the user can plot the step response to reproduce the stability in closed-loop of the synthesized digital controller;
\end{itemize}
%---------------------------------------------------
\subsection{\tool Usage}
%---------------------------------------------------

@@

Users must provide a digital system described as a MATLAB system  using a \texttt{``tf''} (for transfer-function) or an \texttt{``ss''} (for state-space) command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).

\tool is called via command line in MATLAB as \texttt{synthesize(plant, intBits, fracBits, maxRange, minRange)}, where \texttt{plant} is the physical plant in state-space or transfer-function representation, \texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxRange} and \texttt{minRange} are the maximum and minimum dynamic range, respectively.

After executing \texttt{synthesize} command in MATLAB, the output prints the synthesized digital controller according to the digital system representation, {\it i.e.}, transfer-function or state-space equations.

>>>>

\begin{itemize}
\item \textbf{Representation}: the synthesis can be 
performed for digital systems specified as 
transfer-function or state-space equations;
\item \textbf{Fixed-Point Arithmetic}: the digital 
controller is synthesized considering FWL effects, 
in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis can be executed 
via command-line or graphical-user interface (GUI). 
For the GUI application, the user can plot the step response 
to reproduce the stability in closed-loop of the synthesized digital controller;
\end{itemize}

%---------------------------------------------------
\subsection{\tool Usage}
%---------------------------------------------------

@@

Users must provide a digital system described as a MATLAB system 
using a \texttt{tf} (for transfer-function) or an \texttt{ss} (for state-space) 
command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).
\tool is called via command line in MATLAB as

\begin{verbatim}  synthesize(plant, intBits, fracBits, maxR, minR) \end{verbatim}

\noindent where \texttt{plant} is the physical plant in state-space or transfer-function representation, 
\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command in MATLAB, 
\tool provides the synthesized digital controller, according to 
the digital system representation, {\it i.e.}, transfer-function or 
state-space equations.
